\begin{abstract}
Subliminal learning has motivated a token-entanglement hypothesis: semantically
unrelated outputs may transmit hidden traits because their tokens are coupled in
a language model's representation. We test a narrower prerequisite of that
hypothesis---the pre-existing prompting channel linking animal and number
tokens---across tokenizer, model scale, and network depth. Using a fixed
18-animal, 1,110-number protocol, deterministic bootstrap inference,
same-device controls, and full-BF16 Llama models from 1B to 70B parameters, we
find four dissociations. First, bidirectional behavior persists at 70B, but
static animal--number unembedding geometry becomes less predictive of behavior
from Llama-3.1-8B to 70B (paired mean correlation change $-0.080$,
\ci{$-0.127$}{$-0.035$}). Second, a normalized logit-lens trace shows that the
animal answer becomes linearly readable late and follows a similar trajectory
at 8B and 70B (normalized AUC $0.259$ versus $0.269$; paired change $+0.010$,
\ci{$-0.028$}{$+0.045$}). Third, preregistered residual-state patching reveals
a causal handoff from recipient to donor prompt that occurs substantially
earlier at 70B: donor-coefficient causal AUC rises from $0.254$ to $0.540$
(paired change $+0.286$, \ci{$+0.272$}{$+0.300$}); all 18 animal contrasts
increase, while permuted-donor and wrong-animal controls remain small. Fourth,
exact autoregressive scoring does not recover a positive association when Qwen
tokenizes three-digit numbers as digit sequences: the width-3 mean correlation
is $-0.050$ at 0.6B and $-0.048$ at 1.7B. A naive per-target-token normalization
produces a positive association across mixed widths, but it disappears under
within-width control, revealing a sequence-length confound. These results
separate tokenizer atomicity, static output geometry, linear readability, and
causal contextual transmission as distinct properties of the measurable
channel. They characterize a prompting phenomenon and do not show that token
entanglement is necessary for training-time subliminal transfer.
\end{abstract}
