\section{Introduction}
\label{sec:introduction}

Language models can transmit a behavioral trait through training examples that
do not state that trait in ordinary semantic terms. In the canonical example, a
teacher prompted to prefer owls emits lists of numbers; a student fine-tuned on
those lists subsequently exhibits an owl preference
\citep{cloud2025subliminal}. This phenomenon, called \emph{subliminal learning},
raises both a scientific question---what signal is available in apparently
unrelated tokens?---and a practical one---which properties can survive data
filtering and distillation?

One proposed explanation is \emph{token entanglement}: apparently unrelated
tokens can be coupled through model representations and output behavior
\citep{zur2025entanglement}. A striking associated prompting effect links animal
concepts and particular number tokens. Yet ``entanglement'' can refer to several
different objects: a bidirectional behavioral correlation, a static relationship
between rows of the output matrix, or a contextual computation that makes an
animal answer readable from an intermediate hidden state. These objects need not
scale together, and an atomic token measurement may not survive a change of
tokenizer.

We isolate those distinctions using the same 18 animal concepts and 1,110
decimal strings throughout. Our clean scale comparison uses full-BF16
Llama-3.1-8B-Instruct and Llama-3.1-70B-Instruct on CUDA. We separately test
Qwen3-0.6B and Qwen3-1.7B, whose digit-splitting tokenization lets us ask whether
exact multi-token sequence probability repairs an atomic-token probe. Finally,
we trace the Llama channel through every hidden state using the final RMSNorm and
selected output rows as a fixed linear readout, then intervene by transplanting
natural assistant-position residual states between randomly paired number
prompts at five fixed depths.

The experiments support four conclusions. First, the static
geometry--behavior relationship weakens substantially from Llama 8B to 70B,
although behavioral association remains measurable. Second, the contextual
answer trajectory is late-forming and shows no resolved normalized-AUC change
between 8B and 70B. Third, causal donor control emerges much earlier at 70B despite
weaker static geometry: at half depth its conditional coefficient is $0.773$ at
70B versus $0.038$ at 8B. Fourth, full-sequence scoring on Qwen does not restore a positive
width-3 association; moreover, pooling widths and dividing by token count can
manufacture a positive result that vanishes after width control. Thus token
entanglement is not well described by one scalar mechanism that increases with
scale.

Our contribution is deliberately narrower than a theory of training-time
subliminal learning. We provide a controlled map of a pre-existing prompting
channel and show that four measurements commonly treated as interchangeable can
dissociate. Our residual-state intervention establishes causal sufficiency of
the patched assistant state for natural pairwise output differences, while
remaining agnostic about a unique feature, head, neuron, or training-time
mechanism.
