\section{Methods}
\label{sec:methods}

\subsection{Models and comparison structure}

We evaluate Llama-3.2-1B-Instruct and Llama-3.2-3B-Instruct for a descriptive
local ladder, Llama-3.1-8B-Instruct locally and in CUDA BF16, and
Llama-3.1-70B-Instruct in full BF16 across four RTX A6000 GPUs. Because the
low-scale ladder mixes Llama 3.2 and 3.1 releases, our headline scale contrast is
the same-release, same-precision CUDA comparison between Llama-3.1-8B-Instruct
and Llama-3.1-70B-Instruct. A repeated 8B run on MPS and CUDA calibrates device
effects. The multi-token study uses Qwen3-0.6B and Qwen3-1.7B locally.

\subsection{Stimuli and behavioral channel}

The fixed concepts are 18 animals: owl, eagle, dolphin, octopus, elephant,
wolf, lion, tiger, bear, fox, cat, dog, penguin, panda, koala, peacock, shark,
and sea turtle. The Llama protocol contains 1,110 vocabulary tokens that decode
to ASCII decimal strings of width one through three. For each animal $a$ and
number $n$, the forward prompt conditions the model on an animal-preference
system message and scores the number target; the reverse prompt conditions it
on a number-preference system message and scores the first animal target token.
Scores use the protocol's fixed definition
\begin{equation}
  s(t\mid x)=\log\!\left(\operatorname{softmax}(z(x))_t+10^{-12}\right).
\end{equation}
For animal $a$, behavioral entanglement is Pearson's correlation across numbers,
\begin{equation}
  r_a^{\mathrm{beh}}=\operatorname{corr}_{n}
  \left(s(n\mid a),s(a\mid n)\right).
\end{equation}
We report the 18 animal-level values, their median for the behavioral ladder, and
paired animal-level differences for the 8B--70B comparison.

\subsection{Static output geometry}

Let $u_t\in\R^d$ denote the output-unembedding row for token $t$. For an animal
phrase represented by several selected target rows, $u_a$ is their mean. Static
geometry is the raw cosine
\begin{equation}
  g(a,n)=\frac{u_a^\top u_n}{\lVert u_a\rVert\lVert u_n\rVert}.
\end{equation}
For every animal, we correlate $g(a,n)$ across numbers with the saved reverse
behavior $s(a\mid n)$. The preregistered primary statistic is the mean of these
18 correlations. An animal-specificity control subtracts the mean correlation
obtained by the other 17 animals' geometry from the matched-animal correlation.

\subsection{Exact multi-token sequence probe}

Qwen splits the relevant decimal strings into digit sequences rather than the
atomic number words used by Llama. We therefore score all zero-padded strings of
width one, two, and three: $10+100+1000=1{,}110$ targets. A target
$y=(y_1,\ldots,y_k)$ receives exact autoregressive score
\begin{equation}
  S(y\mid x)=\sum_{i=1}^{k}
  \log\!\left(p(y_i\mid x,y_{<i})+10^{-12}\right).
\end{equation}
No separator is prepended. A prefix trie reuses shared computation and agrees
with slow teacher forcing to maximum absolute error $9.24\times10^{-7}$ at 0.6B
and $1.17\times10^{-6}$ at 1.7B. It also regresses to the original selected-token
score for atomic Llama targets.

The preregistered primary analysis restricts to the 1,000 width-3 strings and
correlates complete forward sequence score with reverse animal score. Controls
use only the first target token, compare matched with mismatched animals, analyze
each width separately, and pool widths using sum score, mean score per target
token, or within-width standardization. The width restriction is important
because Qwen's target token count is exactly one, two, or three for the 10, 100,
or 1,000 corresponding strings.

\subsection{Layerwise contextual readout}

For every Llama hidden state $h_{\ell,p}$ at layer $\ell$ and position $p$, we
apply the model's final RMSNorm $N$ followed by the same selected animal output
rows:
\begin{equation}
  q_{\ell,p}(a)=u_a^\top N(h_{\ell,p}).
\end{equation}
Positions are (i) the final assistant position, (ii) the mean of the last
subtoken for each of three number mentions in the system prompt, and (iii) the
last such mention alone. For each layer and animal, we correlate $q_{\ell,p}(a)$
over numbers with saved reverse behavior. We summarize the mean curve using
trapezoidal AUC over relative depth in $[0,1]$ and the earliest relative depth at
which the curve reaches half its final value. The final hidden-state readout
reproduces selected normal logits with zero recorded maximum absolute error.

This is a fixed linear diagnostic. It measures linear readability under the
model's own output head; it neither trains a probe nor establishes causal use.
An animal-specific matched-minus-other readout and the system-number positions
serve as controls.

\subsection{Causal assistant-state patching}

We select 256 unique width-three atomic Llama number strings without inspecting
model outcomes: a seed-0 permutation of the sorted universe supplies 128
unordered pairs, and both directions of each pair are analyzed. The exact pairs
and order are shared across CUDA 8B and 70B. At requested relative depths
$0.25,0.50,0.75,0.90,$ and $0.97$, mapped to the nearest valid transformer-block
input, we replace only the recipient prompt's assistant-position residual state
with the corresponding donor state. All other token positions and subsequent
computation remain those of the recipient. The embedding input supplies an
analytic depth-zero donor coefficient of zero; we never patch the final state.

For animal $a$, let $z_a(n)$ be its selected logit under number prompt $n$ minus
the mean selected logit of the other 17 animals. At every depth we fit, over the
256 ordered observations,
\begin{equation}
 z_a(\operatorname{patch}_{\ell}(d\rightarrow r))=
 \alpha_{a,\ell}+\beta^{d}_{a,\ell}z_a(d)
 +\gamma^{r}_{a,\ell}z_a(r)+\epsilon.
\end{equation}
The donor coefficient $\beta^d$ measures patched-output dependence on the clean
donor contrast while holding the clean recipient contrast fixed; $\gamma^r$
measures retained recipient dependence. We integrate $\beta^d$ over actual
relative depth, including the analytic zero, and normalize by the maximum tested
depth. The primary scale statistic is the paired animal-level 70B-minus-8B
causal-AUC change.

Fixed controls patch a seed-1 derangement of donor numbers, circularly shift the
donor animal label, split pair directions, and patch each recipient state back
into itself. Duplicate clean forwards and identity patches must agree within
$5\times10^{-3}$ selected-logit units. We report full-design condition numbers
and bootstrap degeneracy. An initial local validation exposed shared-recipient
coupling in a subtraction-based slope; the multiple-regression estimand above
was frozen in a transparent amendment before any CUDA or 70B S5 collection.
The invalid original slope remains reported in the supplement.

\subsection{Inference and reproducibility}

Headline descriptive intervals use a fixed seed of 0 and 100,000 bootstrap
resamples over the 18 preregistered animals. Causal intervals use the frozen
20,000-resample crossed bootstrap: animals and 128 unordered pair clusters are
resampled while both directions and exact 8B/70B pairing are retained. We report
all fixed primary and secondary analyses and do not replace primary outcomes
after observing results. Raw collections are atomic and resumable. Saved
artifacts include environment pins, same-device controls, final-logit
regressions, mismatch controls, cloud state, costs, and SHA-256 checksums.
